Sadinle_accuracy

### 2023-07-30 SEI_sensitivity/Sadinle_accuracy_cluster.Rmd

fabl_acc_samps <- matrix(NA, nrow = 5, ncol = 3)
fabl_acc_samps_resolved <- matrix(NA, nrow = 5, ncol = 3)
sad_acc_samps <- matrix(NA, nrow = 5, ncol = 3)

fabl_acc_samps2 <- matrix(NA, nrow = 6, ncol = 3)
fabl_acc_samps_resolved2 <- matrix(NA, nrow = 6, ncol = 3)
sad_acc_samps2 <- matrix(NA, nrow = 6, ncol = 3)

@@

  # Resolution Step
  Zhat_resolved <- ResolveConflicts(Zhat)
  eval_resolved <- GetEvaluations(Zhat_resolved, Ztrue, n1)
  fabl_acc_samps_resolved[, j] <- c(eval_resolved, elapsed[3], overlap)
  fabl_acc_samps[, j] <- c(eval, elapsed[3], overlap)

  #Partial Estimate
  Zhat <- LinkRecordsBK(Zchain[[1]], n1, 1, 1, 2, .1)
  Zhat <- ResolveConflicts(Zhat)
  eval <- GetEvaluations(Zhat, Ztrue, n1)
  RR <- sum(Zhat == -1)/n2
  eval[1] <- sum(Zhat == Ztrue & Ztrue > n1) / (sum(Zhat > n1))
  fabl_acc_samps2[, j] <- c(eval, RR, elapsed[3], overlap)

  #Sadinle 2017 Method
  ptm <- proc.time()
  Zchain <- BRL::bipartiteGibbs(cd)[[1]]
  Zchain <- Zchain[,101:1000]
  elapsed <- proc.time() - ptm
  Zhat <- BRL::linkRecords(Zchain, n1, 1, 1, 2, Inf)
  eval <- GetEvaluations(Zhat, Ztrue, n1)
  sad_acc_samps[, j] <- c(eval, elapsed[3], overlap)

  Zhat <- BRL::linkRecords(Zchain, n1, 1, 1, 2, .1)
  RR <- sum(Zhat == -1)/n2
  eval <- GetEvaluations(Zhat, Ztrue, n1)
  eval[1] <- sum(Zhat == Ztrue & Ztrue > n1) / (sum(Zhat > n1))
  sad_acc_samps2[, j] <- c(eval, RR, elapsed[3], overlap)

@@

>>>>

fabl_acc_samps <- matrix(NA, nrow = 3, ncol = 6)
fabl_acc_samps_resolved <- matrix(NA, nrow = 3, ncol = 6)
sad_acc_samps <- matrix(NA, nrow = 3, ncol = 6)

fabl_acc_samps2 <- matrix(NA, nrow = 3, ncol = 6)
fabl_acc_samps_resolved2 <- matrix(NA, nrow = 3, ncol = 6)
sad_acc_samps2 <- matrix(NA, nrow = 3, ncol = 6)

@@

  # Resolution Step
  Zhat_resolved <- ResolveConflicts(Zhat)
  eval_resolved <- GetEvaluations(Zhat_resolved, Ztrue, n1)
  fabl_acc_samps_resolved[j, ] <- c(eval_resolved, NA, elapsed[3], overlap)
  fabl_acc_samps[j, ] <- c(eval, NA, elapsed[3], overlap)

  #Partial Estimate
  Zhat <- LinkRecordsBK(Zchain[[1]], n1, 1, 1, 2, .1)
  Zhat <- ResolveConflicts(Zhat)
  eval <- GetEvaluations(Zhat, Ztrue, n1)
  RR <- sum(Zhat == -1)/n2
  eval[1] <- sum(Zhat == Ztrue & Ztrue > n1) / (sum(Zhat > n1))
  fabl_acc_samps2[j, ] <- c(eval, RR, elapsed[3], overlap)

  #Sadinle 2017 Method
  ptm <- proc.time()
  Zchain <- BRL::bipartiteGibbs(cd)[[1]]
  Zchain <- Zchain[,101:1000]
  elapsed <- proc.time() - ptm
  Zhat <- BRL::linkRecords(Zchain, n1, 1, 1, 2, Inf)
  eval <- GetEvaluations(Zhat, Ztrue, n1)
  sad_acc_samps[j, ] <- c(eval, NA, elapsed[3], overlap)

  Zhat <- BRL::linkRecords(Zchain, n1, 1, 1, 2, .1)
  RR <- sum(Zhat == -1)/n2
  eval <- GetEvaluations(Zhat, Ztrue, n1)
  eval[1] <- sum(Zhat == Ztrue & Ztrue > n1) / (sum(Zhat > n1))
  sad_acc_samps2[j, ] <- c(eval, RR, elapsed[3], overlap)

@@

fabl_acc_samps <- data.frame(fabl_acc_samps, "fabl") %>% 
  unname() %>% 
  data.frame()
fabl_acc_samps_resolved <- data.frame(fabl_acc_samps_resolved, "fabl_resolved") %>% 
  unname() %>% 
  data.frame()
fabl_acc_samps2 <- data.frame(fabl_acc_samps2, "fabl_partial") %>% 
  unname() %>% 
  data.frame()
sad_acc_samps <- data.frame(sad_acc_samps, "BRL") %>% 
  unname() %>% 
  data.frame()
sad_acc_samps2 <- data.frame(sad_acc_samps2, "BRL_partial") %>% 
  unname() %>% 
  data.frame()

result_df <- rbind(fabl_acc_samps, fabl_acc_samps_resolved, fabl_acc_samps2,
                   sad_acc_samps, sad_acc_samps2)
